---
title: "practical_exercise_2, Methods 3, 2021, autumn semester"
author: 'Rikke Uldbæk'
date: "22/9 2021"
output: pdf_document
---

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, patchwork, ggplot2, lme4, stats)
setwd("~/Desktop/Cognitive Science/3rd semester/Methods 3/github_methods_3/week_02")

```

# Assignment 1: Using mixed effects modelling to model hierarchical data
In this assignment we will be investigating the _politeness_ dataset of Winter and Grawunder (2012) and apply basic methods of multilevel modelling. 

## Dataset
The dataset has been shared on GitHub, so make sure that the csv-file is on your current path. Otherwise you can supply the full path.

```{r}
politeness <- read.csv('politeness.csv') ## read in data
attach(politeness)
```

# Exercises and objectives
The objectives of the exercises of this assignment are:  
1) Learning to recognize hierarchical structures within datasets and describing them  
2) Creating simple multilevel models and assessing their fitness  
3) Write up a report about the findings of the study  

REMEMBER: In your report, make sure to include code that can reproduce the answers requested in the exercises below  
REMEMBER: This assignment will be part of your final portfolio

## Exercise 1 - describing the dataset and making some initial plots

1) Describe the dataset, such that someone who happened upon this dataset could understand the variables and what they contain  
    i. Also consider whether any of the variables in _politeness_ should be encoded as factors or have the factor encoding removed. Hint: ```?factor```  


###Describe the dataset

#####Subject variable
The subject variable represents each participant's individual ID, which makes it easier for us to distinguish between the participants and account for possible individual differences.

Additional information:
This variable is a character string containing 16 different subject ID's, each subject ID contains 14 rows

```{r}
#additional information about subject variable
ls.str(politeness) #general information
length(unique(subject)) #amount of different participants
```

#####Gender variable
The gender variable represents the gender each participant identifies with. "F" corresponds to "Female" and "M" corresponds to "Male".

Additional information: 
56.25% of the participants are Female and 43.75% are Male, which is also visually illustrated by a barplot. 
The variable is binary as it only contains either F or M, and for analytic purposes it will be transformed into a factor variable. 

```{r}
#gender variable plot
barplot(percent_gender,ylim=c(0,100), ylab="percent",main="Barplot of Gender")

#additional information
n <- nrow(politeness)  # Number of rows in total
(percent_gender <- table(politeness$gender)/n * 100) #generating percentages of gender
ls.str(politeness) #general information
politeness$gender <- as.factor(politeness$gender)
```

#####Scenario variable
The scenario variable is an integer-variable and represents 7 different trials/scenarios, where each participant completes each trial/scenario twice, hence 14 rows per participant. Each participants completes these 7 different trials twice as each scenario is either "informal" or "polite".

```{r}
#additional information
ls.str(politeness) #general information
```

#####Attitude variable
The attitude variable is a binary variable containing two options i.e "inf" which corresponds to "informal" and "pol" which corresponds to "formal". Each trial/scenario (n = 14) is either "informal" or "polite", making it 50% "informal" and 50% "polite".

```{r}
#Attitude variable plot
barplot(percent_attitude,ylim=c(0,100), ylab="percent",main="Barplot of Attitude")

#additional information
n <- nrow(politeness)  # Number of rows in total
(percent_attitude <- table(politeness$attitude)/n * 100) #generating percentages of gender
ls.str(politeness) #general information
```

#####Total duration variable
The total duration variable is a numeric variable representing... 

The distribution of the variable is positively skewed (right-skewed distribution).The minimum value in the variable is 0.988 and the maximum value in the variable is 101.375, in addition to this the mean of the variable is 24.176.

```{r}
#total duration variable plot
ggplot(politeness, aes(total_duration))+geom_density()

#additional information
ls.str(politeness) #general information
summary(total_duration)
```

#####F0mn variable
F0mn represents the frequency in Hertz of the voice i.e the pitch in voice in hz. This variable is numeric and the distribution of the data is bimodal. The minimum value in the variable is 80.8 hz and the maximum value in the variable is 415.8 hz, in addition to this the mean of the variable is 197.9 hz. 
```{r}
#f0mn variable plot
ggplot(politeness, aes(f0mn))+geom_density()

#additional information
ls.str(politeness) #general information
summary(f0mn)
```

#####Hiss count variable
The hiss count variable relates to the amount of loud "hissing" breath intake. This variable is an integer variable with a minimum value hissings of 0 and a maximum hissing value of 5. The distribution of the data is positively skewed (right-skewed distribution). 

```{r}
#hiss count variable plot
ggplot(politeness, aes(hiss_count))+geom_density()

#additional information:
ls.str(politeness) #general information
summary(hiss_count)
```


2) Create a new data frame that just contains the subject _F1_ and run two linear models; one that expresses _f0mn_ as dependent on _scenario_ as an integer; and one that expresses _f0mn_ as dependent on _scenario_ encoded as a factor  
    i. Include the model matrices, $X$ from the General Linear Model, for these two models in your report and describe the different interpretations of _scenario_ that these entail
    ii. Which coding of _scenario_, as a factor or not, is more fitting?

Model 1 - scenario as integer
Model 1 expresses f0mn as dependent on scenario as an integer. When the "scenario" variable is integer, it is treated as numeric by R, meaning we would interpret the slope in the summary of the model as follows: per increment of scenario the pitch will go down by 6.886 hz. This is a faulty interpretation, because our model matrix of model 1 shows how we only have 1 linear level, which means we do not look at each scenario individually.

(WHAT THE FUCK)

Model 2 - scenario as factor
Model 2 expresses f0mn as dependent on scenario encoded as a factor. When the "scenario" variable is factor, it is treated categorically by R, which enables us to interpret the output of the model 2 correctly as follows; going from scenario 1 to scenario 2 the pitch increases by 62.40 hz, going from scenario 2 to scenario 3 the pitch increases by 35.35 hz (ER DET HER RIGTIGT?? ELLER SKAL MAN MÅLE MED BASELINE HVER GANG?????????). The model matrix of model 2 shows how we have multiple levels, meaning that we can look at each scenario individually, and thereby investigate their meaning properly. 

Thus, coding the "scenario" variable as factor provides the most accurate information. 

(WHAT THE FUCK)

```{r}
#creating a data frame with only subject F1
df_F1 <- politeness %>% 
  filter(subject == "F1") %>% 
  mutate(scenario_factor = as.factor(scenario))


#model 1 with "f0mn" as y and "scenario" as x (INTEGER) 
class(df_F1$scenario)# it's integer
model_integer <- lm(f0mn~scenario, data=df_F1)
summary(model_integer)

model1_X <- model.matrix(model_integer)
model1_X


#model 2 with "f0mn" as y and "scenario" as x (FACTOR)
class(df_F1$scenario_factor) #its' factor
model_factor <- lm(f0mn~scenario_factor, data=df_F1)
summary(model_factor)

model2_X <- model.matrix(model_factor)
model2_X


#as concluded, coding "scenario" as factor makes most sense
politeness$scenario <- as.factor(politeness$scenario)
```
  

3) Make a plot that includes a subplot for each subject that has _scenario_ on the x-axis and _f0mn_ on the y-axis and where points are colour coded according to _attitude_
    i. Describe the differences between subjects
    
    
```{r}
#plot 
politeness %>% ggplot(aes(x=scenario,y=f0mn, color= subject))+ geom_point()


F1 <- politeness %>% 
  filter(subject== "F1") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F1")

F2 <- politeness %>% 
  filter(subject== "F2") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F2")

F3 <- politeness %>% 
  filter(subject== "F3") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F3")
 
F4 <- politeness %>% 
  filter(subject== "F4") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F4")

F5 <- politeness %>% 
  filter(subject== "F5") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F5")

F6 <- politeness %>% 
  filter(subject== "F6") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F6")

F7 <- politeness %>% 
  filter(subject== "F7") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F7")

F8 <- politeness %>% 
  filter(subject== "F8") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F8")

F9 <- politeness %>% 
  filter(subject== "F9") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject F9")

M1 <- politeness %>% 
  filter(subject== "M1") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject M1")

M2 <- politeness %>% 
  filter(subject== "M2") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject M2")

M3 <- politeness %>% 
  filter(subject== "M3") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject M3")

M4 <- politeness %>% 
  filter(subject== "M4") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject M4")

M5 <- politeness %>% 
  filter(subject== "M5") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject M5")

M6 <- politeness %>% 
  filter(subject== "M6") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject M6")

M7 <- politeness %>% 
  filter(subject== "M7") %>% 
  ggplot(aes(x=scenario,y=f0mn, color= attitude))+ geom_point()+ggtitle("Subject M7")


M7

ggplot(data=politeness, aes(x=scenario,y=f0mn, attitude)) +
  geom_point() +
  facet_grid(subject ~ .)

politeness %>% ggplot(aes(x=scenario, y=f0mn))+
  geom_point(aes(group=subject, color=attitude))+
  stat_summary(fun.y=mean, na.rm=T, group=11, alpha=1, color='red', size=1.5, geom='line')+
  theme_bw()+
  labs(x='year', y='gross profits on assets',
    color=NULL)+theme(legend.position = 'bottom')

```

    
## Exercise 2  - comparison of models

For this part, make sure to have `lme4` installed.  
You can install it using `install.packages("lme4")` and load it using `library(lme4)`  
`lmer` is used for multilevel modelling

```{r, eval=FALSE}
mixed.model <- lmer(formula=..., data=...)
example.formula <- formula(dep.variable ~ first.level.variable + (1 | second.level.variable))
```

1) Build four models and do some comparisons
    i. a single level model that models _f0mn_ as dependent on _gender_
    ii. a two-level model that adds a second level on top of i. where unique intercepts are modelled for each _scenario_
    iii. a two-level model that only has _subject_ as an intercept 
    iv. a two-level model that models intercepts for both _scenario_ and _subject_
    v. which of the models has the lowest residual standard deviation, also compare the Akaike Information Criterion `AIC`?
      - The fourth model (model 4) has the lowest residual standard deviation of 30.65803. 
      - The fourth model (model 4) has the lowest AIC value of 2092.482
    vi. which of the second-level effects explains the most variance?
    
```{r}
#model 1 - single level model that models _f0mn_ as dependent on _gender_
model1 <- lmer(f0mn ~ gender, data=politeness)
summary(model1)
sigma(model1)  #34.49784


#model 2 - two-level model that adds a second level on top of i. where unique intercepts are modelled for each _scenario_
model2 <- lmer(f0mn ~ gender+ (1|scenario), data=politeness)
summary(model2)
sigma(model2)  #38.448

#model 3 - two-level model that only has _subject_ as an intercept 
model3 <- lmer(f0mn ~ gender+ (1|subject), data=politeness)
summary(model3)
sigma(model3)  #32.04287

#model 4 - two-level model that models intercepts for both scenario and subject
model4 <- lmer(f0mn ~ gender + (1|subject) + (1|scenario), data=politeness)
summary(model4)
sigma(model4)  #30.65803 LOWEST


#comparing AIC values
AIC(model1, model2, model3, model4)



#############HVORDAN FANDEN REGNER MAN R2 PÅ MULTIPLE REGRESSION MED RANDOM EFFECTS????????


#calculating R^2  model 2
summary(model2)

Y <- f0mn
X_model2 <- model.matrix(model2)
bhat_model2 <- solve(t(X_model2) %*% X_model2) %*% t(X_model2) %*% Y
X_model2
Y

RSS <- sum((Y-yhat)^2)
SSTO <- sum((Y-yhat)^2) #sum(yi-B0)^2 bog # sum(yi-y mean)^2

#R^2 RSS/SSTO

summary(model1)$r.squared
summary(model2)$adj.r.squared
summary(model3)$adj.r.squared
summary(model4)$adj.r.squared

summary(model2)$r.squared 

summary(modello)$r.squared 


```

2) Why is our single-level model bad?
    i. create a new data frame that has three variables, _subject_, _gender_ and _f0mn_, where _f0mn_ is the average of all responses of each subject, i.e. averaging across _attitude_ and_scenario_
    ii. build a single-level model that models _f0mn_ as dependent on _gender_ using this new dataset
    iii. make Quantile-Quantile plots, comparing theoretical quantiles to the sample quantiles) using `qqnorm` and `qqline` for the new single-level model and compare it to the old single-level model (from 1).i). Which model's residuals ($\epsilon$) fulfil the assumptions of the General Linear Model better?)
    iv. Also make a quantile-quantile plot for the residuals of the  multilevel model with two intercepts. Does it look alright?
3) Plotting the two-intercepts model
    i. Create a plot for each subject, (similar to part 3 in Exercise 1), this time also indicating the fitted value for each of the subjects for each for the scenarios (hint use `fixef` to get the "grand effects" for each gender and `ranef` to get the subject- and scenario-specific effects)
    
## Exercise 3 - now with attitude

1) Carry on with the model with the two unique intercepts fitted (_scenario_ and _subject_).
    i. now build a model that has _attitude_ as a main effect besides _gender_
    ii. make a separate model that besides the main effects of _attitude_ and _gender_ also include their interaction
    iii. describe what the interaction term in the model says about Korean men's pitch when they are polite relative to Korean women's pitch when they are polite (you don't have to judge whether it is interesting)  
2) Compare the three models (1. gender as a main effect; 2. gender and attitude as main effects; 3. gender and attitude as main effects and the interaction between them. For all three models model unique intercepts for _subject_ and _scenario_) using residual variance, residual standard deviation and AIC.  
3)  Choose the model that you think describe the data the best - and write a short report on the main findings based on this model. At least include the following:
  i. describe what the dataset consists of  
  ii. what can you conclude about the effect of gender and attitude on pitch (if anything)?  
  iii. motivate why you would include separate intercepts for subjects and scenarios (if you think they should be included)  
  iv. describe the variance components of the second level (if any)  
  v. include a Quantile-Quantile plot of your chosen model  