---
title: "practical_exercise_5, Methods 3, 2021, autumn semester"
author: 'Rikke Uldbæk'
date: "13/11 2021"
output: pdf_document
---

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("~/Desktop/Cognitive Science/3rd semester/Methods 3/github_methods_3/week_05")
pacman::p_load(tidyverse,dplyr, data.table, vroom, ggplot2, readbulk, lme4, rstanarm, MuMIn, multcomp)

```

# Exercises and objectives
The objectives of the exercises of this assignment are based on: https://doi.org/10.1016/j.concog.2019.03.007  
  
4) Download and organise the data from experiment 1  
5) Use log-likelihood ratio tests to evaluate logistic regression models  
6) Test linear hypotheses  
7) Estimate psychometric functions for the Perceptual Awareness Scale and evaluate them  

REMEMBER: In your report, make sure to include code that can reproduce the answers requested in the exercises below (__MAKE A KNITTED VERSION__)  
REMEMBER: This is part 2 of Assignment 2 and will be part of your final portfolio


# EXERCISE 4 - Download and organise the data from experiment 1

Go to https://osf.io/ecxsj/files/ and download the files associated with Experiment 1 (there should be 29).  
The data is associated with Experiment 1 of the article at the following DOI https://doi.org/10.1016/j.concog.2019.03.007  
  
1) Put the data from all subjects into a single data frame - note that some of the subjects do not have the _seed_ variable. For these subjects, add this variable and make in _NA_ for all observations. (The _seed_ variable will not be part of the analysis and is not an experimental variable)  
    i. Factorise the variables that need factorising  
    ii. Remove the practice trials from the dataset (see the _trial.type_ variable)  
    iii. Create a _correct_ variable  
    iv. Describe how the _target.contrast_ and _target.frames_ variables differ compared to the data from part 1 of this assignment  
    - The target frame is the variable that determines how many frames the target is shown in, i.e for how long the target     is shown. In experiment 1 the target frame ranges from 1-6 and in experiment 2 the target frame is 3 throughout the        entire experiment. 
    - The target contrast variable is a variable that represents the grey-scale proportion of the target digit. In              experiment 1 the target contrast is a fixed number (01) for each participant throughout the entire experiment. In
    experiment 2 the target contrast is adjusted to fit each individual, i.e the each subject has a different target            contrast. 


```{r}
#read the data
df <- read_bulk(
  directory= "experiment_1/",
  fun = read_csv
)

#Get rid of the seed variable
df <- df %>%
  select(!seed)

#Factorize the variables that need factorising  
df$trial.type <- as.factor(df$trial.type)
df$pas <- as.factor(df$pas)
df$trial <- as.factor(df$trial)
df$cue <- as.factor(df$cue)
df$task<- as.factor(df$task)
df$obj.resp <- as.factor(df$obj.resp)
df$subject <- as.factor(df$subject)
df$target.frames <- as.integer(df$target.frames)


#Remove the practice trials from the dataset (see the _trial.type_ variable)  
df<- df %>% 
  subset(trial.type == "experiment")

#Create a _correct_ variable  
df$correct <- (ifelse(df$obj.resp== "o" & df$target.type == "odd","1",
                               ifelse(df$obj.resp=="e" & df$target.type== "even","1", 0)))

```


# EXERCISE 5 - Use log-likelihood ratio tests to evaluate logistic regression models

## Exercise 5.1
1) Do logistic regression - _correct_ as the dependent variable and _target.frames_ as the independent variable. (Make sure that you understand what _target.frames_ encode). Create two models - a pooled model and a partial-pooling model. The partial-pooling model should include a subject-specific intercept.  

### i.Create likelihood function
The likelihood-function for logistic regression is: $L(p)={\displaystyle\prod_{i=1}^Np^{y_i}(1-p)^{(1-y_i)}}$ (Remember the probability mass function for the Bernoulli Distribution). Create a function that calculates the likelihood.  

See chunk.


### ii. Create log-likelihood function
the log-likelihood-function for logistic regression is: $l(p) = {\displaystyle\sum_{i=1}^N}[y_i\ln{p}+(1-y_i)\ln{(1-p)}$. Create a function that calculates the log-likelihood 

See chunk

### iii. Applying the functions 
apply both functions to the pooling model you just created. Make sure that the log-likelihood matches what is returned from the _logLik_ function for the pooled model.Does the likelihood-function return a value that is surprising? 
Why is the log-likelihood preferable when working with computers with limited precision?  

The output of the loglik-function matches my log-likelihood function, they are both -10865.25. Considering the size of the data set, this value is not so surprising, because the likelihood for observing correct (1) is fairly small (and the loglik is super small too). *!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!* 

When using log-likelihood function we avoid getting really small numbers (eg. 10.000's of 0's in a decimal number), so doing this, makes it easier for computers with limited precision to cope with the numbers. *!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!* 


### iv. log-likelihood and partial pooling
now show that the log-likelihood is a little off when applied to the partial pooling model - (the likelihood function is different for the multilevel function - see section 2.1 of https://www.researchgate.net/profile/Douglas-Bates/publication/2753537_Computational_Methods_for_Multilevel_Modelling/links/00b4953b4108d73427000000/Computational-Methods-for-Multilevel-Modelling.pdf if you are interested)  

From the comparison of my loglikelihood-function and the logLik-function it is evident that it's a little off, because the values are not the same. LogLik function when applied on the partial pooling model = -10622.03 (df=3), and when my loglikelihood function is applied to the partial pooling model = -10565.53. 


```{r}
#transform used variables (in order to make code run)
df$correct <- as.numeric(df$correct)

#logistic regression with _correct_ as the dependent variable and _target.frames_ as the independent variable
# complete pooling
complete_pool_model <- glm(correct ~ target.frames, data=df, family=binomial(link = 'logit'))

# partial-pooling model. The partial-pooling model should include a subject-specific intercept.  
partial_pool_model <- glmer(correct ~ target.frames+ (1|subject), data=df, family=binomial(link = 'logit'))


#Create a function that calculates the likelihood  
likelihood <- function(model, y){
  fitted <- fitted.values(model)
  p <- invlogit(fitted)
  return(prod(p^y*(1-p)^(1-y)))
}

likelihood(complete_pool_model, df$correct) # = 0


#Create a function that calculates the log-likelihood  
loglikelihood <- function(model, y){
  p <- fitted.values(model)
  return(sum(y*log(p)+(1-y)*log(1-p)))
         }

loglikelihood(complete_pool_model, df$correct) # = -10865.25 

#comparing with the logLike-function on complete pooling model
logLik(complete_pool_model) # = -10865.25 (df=2)


#using the logLike-function and my log-likelihood-function for partial pooling model
logLik(partial_pool_model) # = -10622.03 (df=3)
loglikelihood(partial_pool_model, df$correct) # = -10565.53

```


## Exercise 5.2
2) Use log-likelihood ratio tests to argue for the addition of predictor variables, start from the null model, `glm(correct ~ 1, 'binomial', data)`, then add subject-level intercepts, then add a group-level effect of _target.frames_ and finally add subject-level slopes for _target.frames_. Also assess whether or not a correlation between the subject-level slopes and the subject-level intercepts should be included.

*!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!* 

*Group-level effect is another word for fixed effect or first-level* -lau

### i.
Write a short methods section and a results section where you indicate which model you chose and the statistics relevant for that choice. Include a plot of the estimated group-level function with `xlim=c(0, 8)` that includes the estimated subject-specific functions.
    ii. also include in the results section whether the fit didn't look good for any of the subjects. If so, identify those subjects in the report, and judge (no statistical test) whether their performance (accuracy) differed from that of the other subjects. Was their performance better than chance? (Use a statistical test this time) (50 %)  


I did not make `xlim=c(0, 8)`, since the target frames range from 1-6. 

*!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!* 


```{r}
#Use log-likelihood ratio tests to argue for the addition of predictor variables
nullmodel <-  glm(correct ~ 1, data=df, family=binomial(link = 'logit'))
model1 <- glmer(correct ~ 1 + (1|subject), data=df,family=binomial(link = 'logit'))
model2 <- glmer(correct ~ target.frames + (1|subject), data=df, family=binomial(link = 'logit'))
model3 <- glmer(correct ~ target.frames + (1+target.frames|subject), data=df, family=binomial(link = 'logit'))
model4 <- glmer(correct ~ target.frames + (1+target.frames||subject), data=df, family=binomial(link = 'logit')) # no correlation model 

#Anova :)) --> cuz it gives the loglikelihood too 
anova(model1, model2,model3, model4, nullmodel)


#Using the log-likelihood ratio test for correlation between the subject-level slopes and the subject-level intercepts
logLik(model4) # -10460.29 (df=4)
logLik(model3) # -10448.83 (df=5)


*!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!* 


#plot of the estimated group-level function with `xlim=c(0, 8)` that includes the estimated subject-specific functions. 
#lav plot hvor vi sammenligner nullmodel med valgte model

df %>% 
  ggplot() +
   geom_smooth(aes(x = target.frames, y = fitted(model3), color = "Partial Pooled model")) + 
   geom_smooth(aes(x = target.frames, y = fitted(nullmodel), color = "Complete Pooled model")) +
   facet_wrap( ~ subject) + 
   labs(title = "Estimated group-level function pr. subject") +
   labs(x = "x = target.frames (1:6)", y = "y = estimated functions (subject level)")

## dette skal i princippet være model 3, men den kan ikke run for mig
```


## Exercise 5.3
3) Now add _pas_ to the group-level effects - if a log-likelihood ratio test justifies this, also add the interaction between _pas_ and _target.frames_ and check whether a log-likelihood ratio test justifies this  
### i. 
If your model doesn't converge, try a different optimizer  

model 6 is great :)), better loglik and better AIC. 

### ii.
Plot the estimated group-level functions over `xlim=c(0, 8)` for each of the four PAS-ratings - add this plot to your report (see: 5.2.i) and add a description of your chosen model. Describe how _pas_ affects accuracy together with target duration if at all. Also comment on the estimated functions' behaviour at target.frame=0 - is that behaviour reasonable?  

I did not make `xlim=c(0, 8)`, since the target frames range from 1-6. 


```{r}
#adding pas as a fixed effect
model5 <- glmer(correct ~ target.frames+pas + (1+target.frames|subject), data=df, family=binomial(link = 'logit'), control = glmerControl(optimizer="bobyqa")) #adding pas as a fixed effect

model6 <- glmer(correct ~ target.frames+pas+ target.frames:pas+ (1+target.frames|subject), data=df, family=binomial(link = 'logit'), control = glmerControl(optimizer="bobyqa")) # adding pas and interaction between pas and target.frames

anova(model5, model6) #model 6's rocks /compared to model5

#Plot the estimated group-level functions over `xlim=c(0, 8)` for each of the four PAS-ratings

df %>% 
  ggplot()+ 
  geom_point((aes(x = target.frames, y = fitted(model6), color=pas)))+
  facet_wrap(.~pas)+ 
  labs(title = "Estimated accurary dependent on target duration and PAS")+
  labs(x = "Target duration (target.frames)", y = "Estimated group-level function")

```


# EXERCISE 6 - Test linear hypotheses

In this section we are going to test different hypotheses. We assume that we have already proved that more objective evidence (longer duration of stimuli) is sufficient to increase accuracy in and of itself and that more subjective evidence *(higher PAS ratings) is also sufficient to increase accuracy in and of itself*.  
We want to test a hypothesis for each of the three neighbouring differences in PAS, i.e. the difference between 2 and 1, the difference between 3 and 2 and the difference between 4 and 3. More specifically, we want to test the hypothesis that accuracy increases faster with objective evidence if subjective evidence is higher at the same time, i.e. we want to test for an interaction.  

## Exercise 6.1
1) Fit a model based on the following formula: `correct ~ pas * target.frames + (target.frames | subject))`


### i. 
First, use `summary` (yes, you are allowed to!) to argue that accuracy increases faster with objective evidence for PAS 2 than for PAS 1. 

plz see the tibble :)))))

```{r}
#Fit a model based on the following formula: `correct ~ pas * target.frames + (target.frames | subject))`
model7 <- glmer(correct~pas*target.frames+ (target.frames|subject), data= df, binomial(link = 'logit'))

summary(model7)

# creating a table showing the percentile increase in accuracy for every fixed effect and interactions
estimates <- c(coef(summary(model7))[1:8])
increase_in_prob <- c(invlogit(estimates))
estimates_text <- c("intercept", "target.frames", "pas2", "pas3", "pas4", "target.frames:pas2", "target.frames:pas3", "target.frames:pas4")
as_tibble(cbind(estimates_text, increase_in_prob)) #comment on these :))

```
    

## Exercise 6.2
2) `summary` won't allow you to test whether accuracy increases faster with objective evidence for PAS 3 than for PAS 2 (unless you use `relevel`, which you are not allowed to in this exercise). Instead, we'll be using the function `glht` from the `multcomp` package


### i. 
To redo the test in 6.1.i, you can create a _contrast_ vector. This vector will have the length of the number of estimated group-level effects and any specific contrast you can think of can be specified using this. For redoing the test from 6.1.i, the code snippet below will do

### ii.
Now test the hypothesis that accuracy increases faster with objective evidence for PAS 3 than for PAS 2.

### iii.
Also test the hypothesis that accuracy increases faster with objective evidence for PAS 4 than for PAS 3

### Snippet for 6.2.i
```{r, eval=FALSE}
## testing whether PAS 2 is different from PAS 1
contrast.vector <- matrix(c(0, 0, 0, 0, 0, 1, 0, 0), nrow=1)
gh <- glht(model7, contrast.vector)
print(summary(gh))

#EXTRA - for my own understanding:
#forklaring af hvorfor contrast.vector 
coef(summary(model7))  # dette specifikke 1-tal står er fordi det er acurracy change fra intercept (pas 1) til pas2:target.frames (pas 2, med interaction)
contrast.vector <- matrix(c(0, 0, 0, 0, 0, 1, 0, 0), nrow=1)


## as another example, we could also test whether there is a difference in
## intercepts between PAS 2 and PAS 3
contrast.vector <- matrix(c(0, -1, 1, 0, 0, 0, 0, 0), nrow=1)
gh <- glht(pas.intact.tf.ranslopeint.with.corr, contrast.vector)
print(summary(gh))

#EXTRA - for my own understanding:
#forklaring af hvorfor contrast.vector 
coef(summary(model7))  # dette specifikke 1-tal og -1-tal står er fordi det er acurracy change fra intercept (pas 1) til pas2:target.frames (pas 2, med interaction)
contrast.vector <- matrix(c(0, -1, 1, 0, 0, 0, 0, 0), nrow=1)
```


## Exercise 6.3
3) Finally, test that whether the difference between PAS 2 and 1 (tested in 6.1.i) is greater than the difference between PAS 4 and 3 (tested in 6.2.iii)


# EXERCISE 7 - Estimate psychometric functions for the Perceptual Awareness Scale and evaluate them  

We saw in 5.3 that the estimated functions went below chance at a target duration of 0 frames (0 ms). This does not seem reasonable, so we will be trying a different approach for fitting here.  
We will fit the following function that results in a sigmoid, $f(x) = a + \frac {b - a} {1 + e^{\frac {c-x} {d}}}$  
It has four parameters: _a_, which can be interpreted as the minimum accuracy level, _b_, which can be interpreted as the maximum accuracy level, _c_, which can be interpreted as the so-called inflexion point, i.e. where the derivative of the sigmoid reaches its maximum and _d_, which can be interpreted as the steepness at the inflexion point. (When _d_ goes towards infinity, the slope goes towards a straight line, and when it goes towards 0, the slope goes towards a step function).  
  
We can define a function of a residual sum of squares as below

```{r, eval=FALSE}
RSS <- function(dataset, par)
{
    ## "dataset" should be a data.frame containing the variables x (target.frames)
    ## and y (correct)
    
    ## "par" are our four parameters (a numeric vector) 
    ## par[1]=a, par[2]=b, par[3]=c, par[4]=d
    x <- dataset$x
    y <- dataset$y
    y.hat <- ## you fill in the estimate of y.hat
    RSS <- sum((y - y.hat)^2)
    return(RSS)
}
```

1) Now, we will fit the sigmoid for the four PAS ratings for Subject 7
    i. use the function `optim`. It returns a list that among other things contains the four estimated parameters. You should set the following arguments:  
    `par`: you can set _c_ and _d_ as 1. Find good choices for _a_ and _b_ yourself (and argue why they are appropriate)  
    `fn`: which function to minimise?  
    `data`: the data frame with _x_, _target.frames_, and _y_, _correct_ in it  
    `method`: 'L-BFGS-B'  
    `lower`: lower bounds for the four parameters, (the lowest value they can take), you can set _c_ and _d_ as `-Inf`. Find good choices for _a_ and _b_ yourself (and argue why they are appropriate)  
    `upper`: upper bounds for the four parameters, (the highest value they can take) can set _c_ and _d_ as `Inf`. Find good choices for _a_ and _b_ yourself (and argue why they are appropriate)    
    ii. Plot the fits for the PAS ratings on a single plot (for subject 7) `xlim=c(0, 8)`
    iii. Create a similar plot for the PAS ratings on a single plot (for subject 7), but this time based on the model from 6.1 `xlim=c(0, 8)`   
    iv. Comment on the differences between the fits - mention some advantages and disadvantages of each way  
2) Finally, estimate the parameters for all subjects and each of their four PAS ratings. Then plot the estimated function at the group-level by taking the mean for each of the four parameters, _a_, _b_, _c_ and _d_ across subjects. A function should be estimated for each PAS-rating (it should look somewhat similar to Fig. 3 from the article:  https://doi.org/10.1016/j.concog.2019.03.007)
    i. compare with the figure you made in 5.3.ii and comment on the differences between the fits - mention some advantages and disadvantages of both.
    
